FATE summary results

### 2019-12-13 paper draft.Rmd
Added unified plankton model plots

```{r, echo=F}
# GOA.ich <- readRDS("/Users/MikeLitzow/Documents/R/Fate/fate-ewi/GOA_ich_7.19.18.one.trend.rds") 
GOA.ich <- readRDS("/Users/MikeLitzow/Documents/github/ewi-in-recovery/ewi-in-recovery/all_plankton_11.20.19.one.trend.rds") 
GOA.ich$summary
```

@@

```{r, echo=F}
all <- readRDS("all_plankton_11.20.19.one.trend.rds") 
all$summary
```

@@

keep <- prop1 > 0.95

@@

plot.a <- ggplot(plot.load, aes(key, value)) +
  theme_bw() +
  geom_violin(fill=cb[3], color=NA) +
  geom_hline(yintercept = 0) +
  theme(axis.title.y = element_blank()) + ylab("Loading") +
  coord_flip() +
  ggtitle("a) Plankton loadings") +
  theme(title = element_text(size=8)) +
  ylim(-2.5,2.5)

@@

plot.c <- ggplot(mod, aes(x=SST)) +
  theme_bw() +
  geom_density(fill=cb[3]) + 
  geom_hline(yintercept=0) + 
  geom_vline(xintercept = 0, lty=2) + 
  xlab("Slope") + 
  ylab("Density") +
  ggtitle(("c) Plankton slope on SST")) +
  theme(title = element_text(size=8))

@@

```{r}
png("combined all plankton time series plots.png", 8, 2.5, units="in", res=300)

ggpubr::ggarrange(plot.a, plot.b, plot.c,
          ncol=3, widths=c(1, 1, 0.8), nrow=1)

>>>>

```{r, echo=F}
# GOA.ich <- readRDS("/Users/MikeLitzow/Documents/R/Fate/fate-ewi/GOA_ich_7.19.18.one.trend.rds") 
GOA.ich <- readRDS("all_plankton_12.11.19.one.trend.rds") 
GOA.ich$summary
```

@@

```{r, echo=F}
all <- readRDS("all_plankton_12.11.19.one.trend.rds") 
all$summary
```

@@

keep <- prop1 > 0.90 # changing to 0.9!

@@

plot.a <- ggplot(plot.load, aes(key, value)) +
  theme_bw() +
  geom_violin(fill=cb[3], color=NA) +
  geom_hline(yintercept = 0) +
  theme(axis.title.y = element_blank()) + ylab("Loading") +
  coord_flip() +
  ggtitle("a) Plankton loadings") +
  theme(title = element_text(size=8)) +
  ylim(-2,2)

@@

plot.c <- ggplot(mod, aes(x=SST)) +
  theme_bw() +
  geom_density(fill=cb[3]) + 
  geom_hline(yintercept=0) + 
  geom_vline(xintercept = 0, lty=2) + 
  xlab("Slope") + 
  ylab("Density") +
  ggtitle(("c) Plankton slope on SST")) +
  theme(title = element_text(size=8)) +
  xlim(-3.2,0.5)

@@

```{r}
png("combined all plankton time series plots.png", 10, 4, units="in", res=300)

ggpubr::ggarrange(plot.a, plot.b, plot.c,
          ncol=3, widths=c(1, 1.3, 0.8), nrow=1)
